An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach

### 2017-10-09 paper/article.tex
ml proof read until validation protocol

As discussed in the previous section, the recognition and the estimation of the level of contribution of sources of interest is of importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}. As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.

>>>>

The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}. As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve an sufficient amount of information to reliably detect the different sound sources of interest.
